On the Gravitational stability of gravito-turbulent accretion disks

### 2016-02-01 paper/results2d.tex
last minute fig add

>>>>

\begin{figure}
  \includegraphics[width=\linewidth,clip=true,trim=0cm 0cm 0cm
    0.0cm]{figures/2dinvisc_theta}
  \caption{
    Growth rates for the 2D inviscid problem as a function of
    the cooling time $\beta$ for two irradiation levels: $\theta=0.1$ (black) and
    $\theta=0.33$ (orange). For each case the vertical dashed-dotted lines mark the cooling times beyond which
    growth rates are longer than 10 orbits. 
    \label{invisc_theta}}
\end{figure}
